Towards a better predictive model from rest fMRI: benchmarks across multiple phenotypes

### 2017-06-13 rs_study/experiments/paper/paper.tex
Update scores with Ward dim=100, 150 on ABIDE

%\subsection{Resting State fMRI (rs-fMRI) prediction pipeline}
\autoref{fig:pipeline}  depicts  our  prediction  pipeline consists of
defining brain ROIs, connectivity parameterization and classification using
machine learning. We used this pipeline to study the various choices
at each
step by measuring the impact of each choice made across diverse prediction
tasks from five different rs-fMRI datasets. In below sections, we outline
about the choices used at each step, rs-fMRI datasets with the prediction task
in each dataset and cross-validation framework to prediction accuracy.

%trategy where at step i), we defined brain ROIs from training set of
%rs-fMRI images where the same set is used for training a linear
%model classifier in prediction tasks at step iii).
\subsection{Definition of brain regions of interest (ROIs)}
There exists many different approaches to define brain ROIs as overviewed
in \cite{thirion2014}. Here, we choose to
define brain ROIs using pre-defined brain atlases based on
anatomical and functional and using data-driven methods. For each type of
defining brain ROIs, we chose six variety of various
choices out of which three
pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
- Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
methods - Linear decomposition models: Group Independent Component
Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
Clustering models: KMeans - Agglomerative with Ward criterion. For each
data-driven method, we build the atlas on training data ($75\%$) on each
split (n=100) and use this atlas for the consecutive step.

>>>>

%\subsection{Resting State fMRI (rs-fMRI) prediction pipeline}
\autoref{fig:pipeline}  depicts  our  functional-connectivity based
prediction  pipeline and consists of
i) defining brain ROIs and extraction of timeseries signals with these
ROIs, ii) connectivity parameterization between pair of ROIs and
iii) connectivity-based classification of phenotypic target using
machine learning.
We rely on this pipeline to study the various choices at each
step in the pipeline by measuring the impact of each choice
made across diverse phenotypic targets from five different
rs-fMRI datasets.

In below sections, we describe about the methods used at each step
in the pipeline, rs-fMRI datasets and the phenotypic target used
within each dataset and cross-validation framework to reporting
prediction accuracy scores.

%trategy where at step i), we defined brain ROIs from training set of
%rs-fMRI images where the same set is used for training a linear
%model classifier in prediction tasks at step iii).
\subsection{Definition of brain regions of interest (ROIs)}
The first step of the pipeline consists in reducing the
dimensionality of the problem by aggregating whole brain voxels into
set of voxels forming a brain ROIs. Each ROI represents a meaningful structure
of the whole brain where we can use this structure to learn the connectivity
interactions to study the classification of phenotypic targets, for instance.
There exists many different kinds of approaches to define brain ROIs
as overviewed in \cite{thirion2014}. We choose to define brain ROIs
using two specific approaches. One approach is using reference atlases
where ROIs are pre-defined while the another approach is
using data-driven methods where ROIs are defined by directly learning
on the data. For each approach, we used various choices in
reference atlases and data-driven methods to study the impact of each
choice in the prediction pipeline on diverse phenotypic targets. The
question underlying atlas selection is whether different brain
disorders lead to a consistent choice, and whether genericity
should be preferred to adaptative strategies.

generated on another anatomical and functional datasets which are not
included in this study. Another approach is using
data-driven methods where ROIs are defined by directly learning on the
data. For each approach, we used various
choices to study the impact of each approach in the prediction pipeline on
diverse prediction tasks.

We outline here various choices used, out of which three are
pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
- Bootstrap Analysis of Stable Clusters (BASC) and four data-driven
methods - Linear decomposition models: Group Independent Component
Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
Clustering models: KMeans - Agglomerative with Ward criterion. For each
data-driven method, we learn ROIs on training set of rs-fMRI images
and
